Xor-Some Preregistered Study: Preprocessing

### 2021-10-24 analysis/main/01_xor-some_prereg_preprocessing_N233.Rmd
preprocess N233 subjects

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N18_anonym.csv")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N18_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N18_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N18_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N18_zScored_wide.csv")
```

>>>>

First, the data is loaded.
```{r, echo=FALSE}
d <- read_csv("./../../data/main/results_73_xor-some-Prolific-main_N233_anonym.csv")

@@

Write out data for plotting:
```{r}
d_test %>% write_csv("./../../data/main/results_prereg_raw_N233_test.csv")
```

@@

Write out tidy data:
```{r}
d_full_clean %>% write_csv("./../../data/main/results_prereg_N233_tidy.csv")
```

@@

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_N233_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_N233_zScored_wide.csv")
```
